---
title: "MoharanaPraparna_ProjectPartE_BusinessQueries"
author: "PRAPARNA"
date: "20/12/2021"
output: html_document
---

```{r setup}
library(knitr)
library(DBI)
library(RSQLite)

knitr::opts_chunk$set(echo = TRUE)

Story = dbConnect(RSQLite::SQLite(), dbname = "MoharanaPraparna_ProjectPartE_DataBaseFile.db")

knitr::opts_chunk$set(connection = Story)
```

```{r }
DBI::dbListTables(Story)
```

**1. Users can check for specific Genre of book and view details of the book.**
```{sql connection=Story, max.print=-1}
SELECT BOOK_NAME,GENRE
FROM BOOKS
JOIN BOOK_GENRE ON BOOKS.BOOK_ID=BOOK_GENRE.BOOK_ID
JOIN GENRE ON GENRE.GENRE_ID=BOOK_GENRE.GENRE_ID
WHERE GENRE = 'FICTION'
```

**2.The user can search for specific book name and view details about it.**
```{sql connection=Story, max.print=-1}
SELECT BOOK_NAME,(AUTHOR_FIRST_NAME||""||AUTHOR_LAST_NAME) AS AUTHOR_FULLNAME,BOOK_RATING,TRACK_RATING
FROM BOOKS
JOIN BOOK_AUTHORSHIP ON BOOKS.BOOK_ID=BOOK_AUTHORSHIP.BOOK_ID
JOIN AUTHOR ON BOOK_AUTHORSHIP.AUTHOR_ID=AUTHOR.AUTHOR_ID
WHERE BOOK_NAME LIKE '%ALCHEMIST%';
```

**3.The user can view recommendations such Best_Sellers,Latest_releases and view list of books related to Recommendation by genre and publication year**
```{sql connection=Story, max.print=-1}
SELECT BOOK_NAME,RECOMMENDATION,GENRE,PUBLICATION_YEAR
FROM BOOKS
JOIN BOOK_GENRE ON BOOKS.BOOK_ID=BOOK_GENRE.BOOK_ID
JOIN GENRE ON GENRE.GENRE_ID=BOOK_GENRE.GENRE_ID
WHERE RECOMMENDATION = 'BEST_SELLERS'
ORDER BY PUBLICATION_YEAR AND GENRE
```

**4.User can update instagram id as user might change instagram id in future**
```{sql connection=Story, max.print=-1}
UPDATE INSTAGRAM
SET INSTAGRAM_ID ='HeLlY**90'
WHERE USER_ID = 105;
```

**5.User can see for top 3 highest rated books by genre**
```{sql connection=Story, max.print=-1}
SELECT BOOK_NAME,BOOK_RATING,GENRE
FROM BOOKS
JOIN BOOK_GENRE ON BOOKS.BOOK_ID=BOOK_GENRE.BOOK_ID
JOIN GENRE ON GENRE.GENRE_ID=BOOK_GENRE.GENRE_ID
ORDER BY BOOK_RATING DESC 
LIMIT 3
```

**6.Users can view the List of Stories and information related to it**
```{sql connection=Story, max.print=-1}
SELECT STORIES,NUMBER_OF_EPISODES,DURATION,EPISODES_NO_1,EPISODES_NO_2,EPISODES_NO_3,EPISODES_NO_5
FROM SERIES;
```

**7.Admin can view which User who have taken subscription plans 99**
```{sql connection=Story, max.print=-1}
SELECT USER_NAME, USER_EMAIL, USER_MOBILE, SUBSCRIPTION_PLAN
FROM USER
WHERE SUBSCRIPTION_PLAN == 99
```

**8. Displaying the books which have less rating than three and not rated books as newly released (EXCEPT clause is used to display the result which could not be displayed in second SELECT statement)** 
```{sql connection=Story, max.print=-1}
SELECT BOOK_NAME,BOOK_RATING,GENRE
FROM BOOKS
JOIN BOOK_GENRE ON BOOKS.BOOK_ID=BOOK_GENRE.BOOK_ID
JOIN GENRE ON GENRE.GENRE_ID=BOOK_GENRE.GENRE_ID

EXCEPT

SELECT BOOK_NAME,BOOK_RATING,GENRE
FROM BOOKS
JOIN BOOK_GENRE ON BOOKS.BOOK_ID=BOOK_GENRE.BOOK_ID
JOIN GENRE ON GENRE.GENRE_ID=BOOK_GENRE.GENRE_ID
GROUP BY BOOK_NAME HAVING BOOK_RATING > 3.0
```

**9.The Admin can view user who have select kids mode filter without invading the privacy of users**
```{sql connection=Story, max.print=-1}
DROP VIEW IF EXISTS KIDSMODE
```

```{sql connection=Story, max.print=-1}
CREATE VIEW [KIDSMODE] AS
SELECT USER_NAME,USER_EMAIL,USER_MOBILE,KIDSMODE
FROM LOGIN
JOIN USER ON LOGIN.USER_ID=USER.USER_ID
```

```{sql connection=Story, max.print=-1}
SELECT USER_NAME,USER_EMAIL,USER_MOBILE,KIDSMODE FROM [KIDSMODE];
```

**10.Ranking of Books according to rating and genre.**
```{sql connection=Story, max.print=-1}
SELECT BOOK_NAME,BOOK_RATING,GENRE,
RANK() OVER (
	PARTITION BY GENRE
	ORDER BY BOOK_RATING) Ranking
FROM BOOKS
JOIN BOOK_GENRE ON BOOKS.BOOK_ID=BOOK_GENRE.BOOK_ID
JOIN GENRE ON GENRE.GENRE_ID=BOOK_GENRE.GENRE_ID
```

**11.Admin can view user country and their proficiency level of language as well as language used by them to access the storytel application**
```{sql connection=Story, max.print=-1}
SELECT USER_NAME,COUNTRY,PRIMARY_LANGUAGE,SECONDARY_LANGUAGE,SKILL_LEVEL
FROM USER
JOIN USER_LANGUAGES ON USER.USER_ID=USER_LANGUAGES.USER_ID
JOIN LANGUAGE ON USER_LANGUAGES.LANGUAGE_ID=LANGUAGE.LANGUAGE_ID
JOIN COUNTRY ON COUNTRY.COUNTRY_ID=USER.COUNTRY_ID
```

**12.User can view ranking of books according to specific genre**
```{sql connection=Story, max.print=-1}
WITH Genre_Rank AS (SELECT BOOK_NAME,BOOK_RATING,GENRE
FROM BOOKS
JOIN BOOK_GENRE ON BOOKS.BOOK_ID=BOOK_GENRE.BOOK_ID
JOIN GENRE ON GENRE.GENRE_ID=BOOK_GENRE.GENRE_ID
WHERE GENRE = 'FICTION')

SELECT BOOK_NAME,BOOK_RATING,GENRE,
RANK() OVER (
	PARTITION BY GENRE
	ORDER BY BOOK_RATING DESC) Ranking
FROM Genre_Rank
```
